\huge{Comment on `The Limits of Cosmic Shear'}

### 2016-12-05 cfhtlens.tex
added JHD's comments and sections on CMB Lensing and Nbody sims

The Canada-France-Hawaii Telescope Lensing Survey (CFHTLenS) represented a major step forward for the field of weak gravitational lensing, in terms of improved accuracy in data reduction \citep{erben/etal:2013}, the implementation of Gaussianised matched multi-band photometry \citep{hildebrandt/etal:2012}, cross-correlation clustering analysis between photometric redshift slices to verify tomographic redshift distributions \citep{benjamin/etal:2013}, accurate calibrated shape measurements \citep{miller/etal:2013} and a full suite of informative systematic tests to select a clean data set \citep{heymans/etal:2012}.    Since the public release of this survey in 2013, the community has continued to scrutinise and advance our understanding of CFHTLenS by identifying a number of areas where the analysis could improve:
\begin{itemize}
\item{\citet{choi/etal:2016} identified biases in the tomographic photometric redshift distributions using a more effective clustering analysis, in comparison to \citet{benjamin/etal:2013}, by incorporating newly overlapping spectroscopy from the Sloan Digital Sky Survey.  The CFHTLenS tomographic cosmological analysis was then revisited by \citet{joudaki/etal:2016} in order to include a full redshift error analysis based on the results from \citet{choi/etal:2016}, discussed further in section~\ref{sec:photoz}.}
\item{\citet{asgari/etal:2016} used the stringent `COSEBI' statistic to identify significant non-lensing `B-mode' distortions when the CFHTLenS data was split into tomographic slices.}
\item{\citet{kuijken/etal:2015} showed that the CFHTLenS shear calibration corrections derived in \citet{miller/etal:2013} were underestimated as a result of an imperfect match between the galaxy populations in the data and image simulations.}
\item{\citet{fenechconti/etal:2016} demonstrated that the CFHTLenS data would have been subject to a weight bias that favours galaxies that are more intrinsically oriented with the point-spread function.}
\item{\citet{joudaki/etal:2016} updated the CFHTLenS covariance matrices using larger-box numerical simulations that were less subject to the lack of power on large scales.}
\end{itemize}
All these advances in our understanding were incorporated and accounted for in the recent KiDS cosmic shear analysis \citep{hildebrandt/etal:2016} which reports a $2.3 \sigma$ tension with Planck.  Efforts are now underway to fully re-analyse CFHTLenS using the advanced KiDS analysis pipeline with revised shape measurements and calibrations for the shear and photometric redshifts.

@@

We repeated the `one-parameter' analysis for the full range of Limber cases listed in Table~\ref{tab:Tl_nu} finding the lowest conditional value of $\sigma_8 = XXX \pm XXX$ for the XXX case and the highest conditional value of $\sigma_8 = XXX \pm XXX$ for the XXX case.  As expected from the comparison in Figure~\ref{fig:Cl_xi} the different combinations of assuming flat or spherical sky, or baseline of extended Limber make little difference to the cosmological parameter constraints, even in this exaggerated `one-parameter' analysis.

@@

>>>>

The Canada-France-Hawaii Telescope Lensing Survey (CFHTLenS) represented a major step forward for the field of weak gravitational lensing, in terms of improved accuracy in data reduction \citep{erben/etal:2013}, the implementation of Gaussianised matched multi-band photometry \citep{hildebrandt/etal:2012}, cross-correlation clustering analysis between photometric redshift slices to verify tomographic redshift distributions \citep{benjamin/etal:2013}, accurate calibrated shape measurements \citep{miller/etal:2013} and a full suite of informative systematic tests to select a clean data set \citep{heymans/etal:2012}.    Since the public release of this survey in 2013, the community has continued to scrutinise and advance our understanding of CFHTLenS by identifying a number of areas where analyses could improve:
\begin{itemize}
\item{\citet{choi/etal:2016} identified biases in the tomographic photometric redshift distributions using a more effective clustering analysis, in comparison to \citet{benjamin/etal:2013}, by incorporating newly overlapping spectroscopy from the Sloan Digital Sky Survey.  The CFHTLenS tomographic cosmological analysis was then revisited by \citet{joudaki/etal:2016} in order to include a full redshift error analysis based on the results from \citet{choi/etal:2016}, discussed further in section~\ref{sec:photoz}.}
\item{\citet{asgari/etal:2016} used the stringent `COSEBI' statistic to identify significant non-lensing `B-mode' distortions when the CFHTLenS data was split into tomographic slices.}
\item{\citet{kuijken/etal:2015} showed that the CFHTLenS shear calibration corrections derived in \citet{miller/etal:2013} were underestimated as a result of an imperfect match between the galaxy populations in the data and image simulations.}
\item{\citet{fenechconti/etal:2016} demonstrated that the CFHTLenS data would have been subject to a weight bias that favours galaxies that are more intrinsically oriented with the point-spread function.}
\item{\citet{joudaki/etal:2016} updated the CFHTLenS covariance matrices using larger-box numerical simulations that were less subject to the lack of power on large scales.}
\end{itemize}
All these advances in our understanding were incorporated and accounted for in the recent KiDS cosmic shear analysis \citep{hildebrandt/etal:2016} which reports a $2.3 \sigma$ tension with Planck.  Efforts are now underway to fully re-analyse CFHTLenS using the advanced KiDS analysis pipeline with revised shape measurements and calibrations for the shear and photometric redshifts.

@@

We repeated the `one-parameter' analysis for the full range of Limber cases listed in Table~\ref{tab:Tl_nu} finding the lowest conditional value of $\sigma_8 = XXX \pm XXX$ for the XXX case and the highest conditional value of $\sigma_8 = XXX \pm XXX$ for the XXX case.  As expected from the comparison in Figure~\ref{fig:Cl_xi} the different combinations of assuming flat or spherical sky, or baseline of extended Limber make little difference to the cosmological parameter constraints, even in this `one-parameter' analysis.

@@

\subsection{On the Validation of Methods on Simulations}
It is discussed in \citet{kitching/etal:2016} that the validation of cosmic shear estimators on mock catalogues could also be affected by the approximations they investigate.  We agree that a full sky mock should be compared to a full curved sky non-Limber prediction.  It is then suggested, however, that the discrepancies already reported between existing mocks and the predictions could be attributed to these approximations, as opposed to a finite box effect \citep{kiessling/etal:2011, harnois-deraps/etal:2012, harnois-deraps/vanwaerbeke:2015}.  Going beyond flat sky and Limber could improve the agreement, however this cannot explain the results of \citet{harnois-deraps/vanwaerbeke:2015} who demonstrate that the large scale under-estimation of power varies with the simulation box size. This volume effect was verified by comparing explicitly the $\xi_+$ statistic at large angular scales between simulation volumes with box sides = 147Mpc/h and 515Mpc/h \citep[see Fig. 5 in][]{harnois-deraps/vanwaerbeke:2015}. The increase of power loss with decreasing box size was shown to be fully-modelled by excluding the super-box $k$-modes in the Limber predictions, something that the approximations discussed in \citet{kitching/etal:2016} would be unable to explain.

We note that any future comparison of mock data with full curved sky non-Limber predictions will place requirements on the input weak lensing simulations.  Many currently work with parallel plane mass-sheets as opposed to curved sky mass-sheets and at large angles, these two approaches differ regardless of the box size.

\subsection{On the application to CMB lensing}
\citet{kitching/etal:2016} argue that their correction to the Limber and flat sky approximations would also affect predictions involving the shear and convergence cross-spectrum, such that CMB lensing - galaxy lensing cross-correlation should include a pre-term $[\ell/(\ell+0.5)]^4$.   We have verified that this term would have negligible impact on the current measurements, given the relatively low signal to noise ratio. For example, most measurements \citep{hand/etal:2015, liu/hill:2015, kirk/etal:2016,harnois-deraps/etal:2016} are carried over angular multipoles in the range $\ell \in [20-2000]$, and are organized in $\sim$ five bins. The size of the pre-term $[\ell/(\ell+0.5)]^4$, averaged over the first bin, is of the order of 2\%, and then becomes sub-percent for all other bins. In comparison, the size of the statistical error bars are of the order 25-35\% with additional uncertainty due to photometric redshifts (10-15\%) and intrinsic galaxy alignments (10-15\%).
